SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/experiments.tex
add

We have implemented the encodings for each variants
using the python interface of $\zthree$ in a tool.
%
Our tool allows the user to choose a model and the size of the network
besides other parameters like connectivity and number of parallel
edges.
%
It uses Z3 Python interface to build the needed constraints and
applies $\zthree$ solver on the constraints to find a model (
a satisfying assignment that respects the constraints).
%
This tool also translates the satisfying model found by $\zthree$ into
a VTS and presents a visual output to the user in form of annotated graph.
%
% The output graph will satisfy the underlying rules of the system, so
% it always is a valid vesicle transport network.
%
% The resultant graph provides an overview of the underlying VTS
% where directed labeled edges and nodes provide the
% complete information about the system.
%
We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.

@@

In Table~\ref{tab:qf-grabh}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM.
%
We have compared our performance with the performance of our earlier 
CBMC based implementation.
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Hence with the use of this novel encoding, we are able to scale the
system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments. \textbf{Not only we have improved finding a SAT model but this encoding also did better in comparison to cbmc in the
case of refutation that no model exists. Refer table variant A timing
comparison and VARIANT D with N =2.}
%
% \ankit{
% This additional scalability can provide us leverage to ask for related
% open questions that were not previously possible, for example, what is
% the minimum number of molecules required to satisfy the vesicular
% traffic system in eukaryotes.}
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.

>>>>

We have implemented the encodings for each variants
using the python interface of $\zthree$ in a tool (A'tool).
%
Our tool allows the user to choose a model and the size of the network
besides other parameters like connectivity and number of parallel
edges.
%
It uses Z3 Python interface to build the needed constraints and
applies $\zthree$ solver on the constraints to find a model (
a satisfying assignment that respects the constraints).
%
This tool also translates the satisfying model found by $\zthree$ into
a VTS and presents a visual output to the user in form of annotated graph.
%
% The output graph will satisfy the underlying rules of the system, so
% it always is a valid vesicle transport network.
%
% The resultant graph provides an overview of the underlying VTS
% where directed labeled edges and nodes provide the
% complete information about the system.
%
We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.

@@

In Table~\ref{tab:qf-grabh}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM.
%
We have compared our performance with the performance of our earlier 
CBMC based implementation (O'cbmc).
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
 \textbf{Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2).}. Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments.
%
% \ankit{
% This additional scalability can provide us leverage to ask for related
% open questions that were not previously possible, for example, what is
% the minimum number of molecules required to satisfy the vesicular
% traffic system in eukaryotes.}
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.
